Loading and preprocessing the data
```{r, echo=TRUE, eval=TRUE}
data <- read.csv("C:/Users/PCPC/Desktop/activity.csv")
```

# What is mean total number of steps taken per day?

1. Histogram of the total number of steps taken each day.

```{r, echo=TRUE, eval=TRUE}
new_day_step <- aggregate(steps ~ date, data, sum)
hist(new_day_step$steps, col = "orange")
```

2. The mean and median total number of steps taken per day.

```{r, echo=TRUE, eval=TRUE}
mean(new_day_step$steps, na.rm = TRUE)

```

```{r, echo=TRUE, eval=TRUE}
median(new_day_step$steps, na.rm = TRUE)

```

# What is the average daily activity pattern?

1. Time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r, echo=TRUE, eval=TRUE}
new_day_step_interval <- aggregate(steps ~ interval, data, mean)
plot(new_day_step_interval$interval, new_day_step_interval$steps, 
    type = "l", col= "orange")


```

2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r, echo=TRUE, eval=TRUE}

new_day_step_interval[new_day_step_interval$steps == max(new_day_step_interval$steps), ]
```

# Imputing missing values

1. Total number of missing values in the dataset

```{r, echo=TRUE, eval=TRUE}
sum(is.na(data$steps))
```

2. Strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. For example, you could use the mean/median for that day, or the mean for that 5-minute interval, etc.

```{r, echo=TRUE, eval=TRUE}
new_data <- na.omit(data)
head(new_data)
```

Histogram of the total number of steps taken each day
```{r, echo=TRUE, eval=TRUE}
new_data_steps <- aggregate(steps ~ date, new_data, sum)
hist(new_data_steps$steps, col = "orange")
```

Mean and median of total number of steps taken per day

```{r, echo=TRUE, eval=TRUE}
mean(new_data_steps$steps)
```

```{r, echo=TRUE, eval=TRUE}
median(new_data_steps$steps)
```

# Are there differences in activity patterns between weekdays and weekends?

1. Create a new factor variable in the dataset with two levels - “weekday” and “weekend” indicating whether a given date is a weekday or weekend day.

```{r, echo=TRUE, eval=TRUE}
library(lattice)
data <- data.frame(day = weekdays(as.Date(data$date)), daystatus = "NA", 
    data)
data$daystatus <- factor(ifelse(data$day %in% c("Saturday", 
    "Sunday"), "weekend", "weekday"))


```
